Molecular dynamics simulation of synchronization in driven particles

### 2021-01-31 manuscript/manuscript_ajp_2020.tex
fixed some Brownian commentary and equations

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$. [{\it I believe the slight slope in this curve is due to sampling - where does the particle start/end ?}]}
\label{fig:1}
\end{figure}
\end{center}

@@

%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion 
  is a temperature and viscosity dependent
  phenomena in which 
  particles change direction %randomly
  due to collisions with fluid particles.
  The frequency of collisions depends on the properties of
  the suspending fluid.
  These collisions are more likely at higher temperature
  due to the increased kinetic energy of the fluid particles,
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations temperature effects
  can be modeled by including randomized forces $f^T$
  to emulate the motion of particles undergoing Brownian motion.
  A distribution of random forces contributes equally in all
  directions such that the force averaged over a finite time interval
  is zero $\langle f^T(t) \rangle = 0$.
  Random distributions are not correlated 
  over the independent variable,
  where we take our independent variable to be time 
  $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$
  for a system with 
  energy $k_B T$
  derived from the Boltzmann constant $k_B$
  and temperature $T$ \cite{Allen2017}.
  A particle
  with energy $k_b T_{min} > U_0$ may 
  hop over landscape
  barriers.

@@

  La la la...

>>>>

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$. }
\label{fig:1}
\end{figure}
\end{center}

@@

%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion 
  is a temperature and viscosity dependent
  phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The frequency of collisions depends on the properties of
  the suspending fluid.
  At higher temperatures
  the increased kinetic energy of particles
  makes collisions more likely, 
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations temperature effects
  can be modeled with randomized forces $f^T$
  to emulate the motion of particles undergoing Brownian motion.
  A random distribution of forces
  causes motion
  equally in all
  directions such that the force averaged over a finite time interval
  is zero
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  where $n$ is an integer indicating
  discrete simulation timesteps
  such that $t = N \Delta t$.
  Random distributions are not correlated 
  over the independent variable,
  for the independent variable to be time
  \begin{equation}
  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  \end{equation}
  for times $t$ and $\tau$,
  where $\delta(t-\tau)$ is the Dirac-delta function.
  Here the scaling factor energy of 
  $k_B T$ is
  derived from the Boltzmann constant $k_B$
  and temperature $T$ \cite{Allen2017}.
  A particle
  with energy $k_b T_{min} > U_0$ may 
  hop over landscape
  barriers.

@@

  A range of interesting behaviors
  can be explored by varying the
  relative strength of the confining landscape
  and external driving force.
